A Theory for Data Migration of Information Systems

### 2022-09-25 2022 Migration/articleMigration.tex
minor cleanup

	We use two datasets: $\dataset=$ and $\dataset'=$.
	Before doing so, let us first define the disjoint union of two information systems.
\begin{definition}[disjoint union of datasets]
\begin{eqnarray}
	\la\atoms,\concepts,\inst,\isa,\rels,\triples\ra\sqcup\la\atoms',\concepts',\inst',\isa',\rels',\triples'\ra
\end{eqnarray}
\begin{eqnarray}
	\omit\rlap{Some text that I want to appear here...}\\
	&=&\la\atoms\uplus\atoms',\ \concepts\uplus\concepts',\ \inst\uplus^2\inst',\ \isa\uplus^2\isa',\ \rels\uplus^3\rels',\ \triples\uplus^5\triples'\ra\\
		X\uplus Y&=&\{(x,0)|\ x\in X\}\ \cup\ \{(y,1)|\ y\in Y\}\\
		X\uplus^2 Y&=&\begin{array}[t]{@{}l}\{((x_1,0),(x_2,0))|\ (x_1,x_2)\in X\}\ \cup\\ \{((y_1,1),(y_2,1))|\ (y_1,y_2)\in Y\}\end{array}\\
		X\uplus^3 Y&=&\begin{array}[t]{@{}l}\{\declare{(n,0)}{(A,0)}{(B,0)}\mid\ \declare{n}{A}{B}\in X\}\ \cup\\ \{\declare{(n,1)}{(A,1)}{(B,1)}\mid\ \declare{n}{A}{B}\in Y\}\end{array}\\
		X\uplus^5 Y&=&\begin{array}[t]{@{}l}\{\triple{(a,0)}{\declare{(n,0)}{(A,0)}{(B,0)}}{(b,0)}\mid\ \triple{a}{\declare{n}{A}{B}}{b}\in X\}\ \cup\\ \{\triple{(a,1)}{\declare{(n,1)}{(A,1)}{(B,1)}}{(b,1)}\mid\ \triple{a}{\declare{n}{A}{B}}{b}\in Y\}\end{array}
\end{eqnarray}
\end{definition}
Note that if $\dataset$ and $\dataset'$ are datasets, then so is $\dataset\sqcup\dataset'$.

>>>>

	We use two datasets: $\dataset$ and $\dataset'$.
	Before doing so, let us first define the disjoint union of two information systems.
\begin{definition}[disjoint union of datasets]
\begin{eqnarray}
	\omit\rlap{$\la\atoms,\concepts,\inst,\isa,\rels,\triples\ra\sqcup\la\atoms',\concepts',\inst',\isa',\rels',\triples'\ra$}\notag\\
	&=&\la\atoms\uplus\atoms',\ \concepts\uplus\concepts',\ \inst\uplus^2\inst',\ \isa\uplus^2\isa',\ \rels\uplus^3\rels',\ \triples\uplus^5\triples'\ra\notag\\
		X\uplus Y&=&\{(x,0)|\ x\in X\}\ \cup\ \{(y,1)|\ y\in Y\}\\
		X\uplus^2 Y&=&\begin{array}[t]{@{}l}\{((x_1,0),(x_2,0))|\ (x_1,x_2)\in X\}\ \cup\\ \{((y_1,1),(y_2,1))|\ (y_1,y_2)\in Y\}\end{array}\\
		X\uplus^3 Y&=&\begin{array}[t]{@{}l}\{\declare{(n,0)}{(A,0)}{(B,0)}\mid\ \declare{n}{A}{B}\in X\}\ \cup\\ \{\declare{(n,1)}{(A,1)}{(B,1)}\mid\ \declare{n}{A}{B}\in Y\}\end{array}\\
		X\uplus^5 Y&=&\begin{array}[t]{@{}l}\{\triple{(a,0)}{\declare{(n,0)}{(A,0)}{(B,0)}}{(b,0)}\mid\ \triple{a}{\declare{n}{A}{B}}{b}\in X\}\ \cup\\ \{\triple{(a,1)}{\declare{(n,1)}{(A,1)}{(B,1)}}{(b,1)}\mid\ \triple{a}{\declare{n}{A}{B}}{b}\in Y\}\end{array}
\end{eqnarray}
\end{definition}
Note that if $\dataset$ and $\dataset'$ are datasets, then so is $\dataset\sqcup\dataset'$.
